% Sam's Kaplan's resume, as of Feb 24 2011
% TODO: Fix line spacing between multiple line cvlistitems
% TODO: Change colors: current blue is too light when printed

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\usepackage{fullpage}
\moderncvtheme[blue]{classic}

\firstname{Sam}
\familyname{Kaplan}
\address{104 E. Jefferson St.}{Media, PA 19063}
\mobile{(484) 437-2799}
\email{stkaplan@gmail.com}

\newcommand{\placeholder}{\textcolor{red}{[ADD MORE INFO]}}

\nopagenumbers{}
\usepackage[none]{hyphenat}

\setlength{\hintscolumnwidth}{3.5cm}

\begin{document}
\maketitle
\section{Skills}
\cvline{Languages:}{C, C++, Java, C$\sharp$, Ruby, Python, bash}
\cvline{Software:}{Visual Studio, Eclipse, Vim, git, Subversion, Mercurial, LLVM/clang, gcc, gdb, SQL, \LaTeX}

\section{Work Experience}
\cventry{Jul 2012 -- Present}{\textcolor{red}{Job Title}}{ET International, Inc.}{Newark, DE}{}{}
\cvlistitem{Contributed to language design of SCALE extension of C.}
\cvlistitem{Worked on translator of SCALE programs to standard C.}

\cventry{Sep 2011 -- Jul 2012}{\textcolor{red}{Job Title}}{ET International, Inc.}{Newark, DE}{}{}
\cvlistitem{Ported and optimized SWARM parallel programming framework to Intel Runnemede architecture.}
\cvlistitem{Measured power-efficiency of simulated Runnemede architecture.}
\cvlistitem{Implemented parallelized Cholesky decomposition and matrix multiplication algorithms for use as benchmarks.}
\cvlistitem{Collaborated with research team at Intel.}

\cventry{Feb 2011 -- Sep 2011}{Test Engineer}{ET International, Inc.}{Newark, DE}{}{}
\cvlistitem{Wrote tests to demonstrate completion and effectiveness of Cyclops64 supercomputer.}
\cvlistitem{Implemented requirement tests and regression tests in Python and Bash.}
\cvlistitem{Diagnosed hardware, software, and scalability problems in supercomputer installations containing up to 3000 nodes.}
\cvlistitem{Provided on-site customer support to government customer.}

\cventry{Dec 2009 -- Feb 2011}{Compiler Engineer}{ET International, Inc.}{Newark, DE}{}{}
\cvlistitem{Implemented dynamic optimizers in C++ for source-to-source C compiler using LLVM and ROSE libraries.}
\cvlistitem{Worked on a Chaitin-Briggs register allocator implemented in LLVM.}
\cvlistitem{Collaborated with researchers at Rice University and Ohio State University.}
\cvlistitem{Coordinated with team of developers using git for version control.}
\cvlistitem{Used Hudson and Buildbot for continuous integration.}
\cvlistitem{Wrote automated unit test suites with GNU Autotest.}

\cventry{Nov 2007 -- Aug 2008}{Software Developer}{FMP Media Solutions}{Conshohocken, PA}{}{}
\cvlistitem{Redeveloped and relaunched digital video production company's website.}
\cvlistitem{Created a database front-end on website to display and allow employees to enter news articles.}
\cvlistitem{Wrote C$\sharp$ modules for DotNoteNuke CMS for use on company's website and intranet.}
\cvlistitem{Worked with a SQL Server database as backend for DotNetNuke.}

\cventry{Summer 2007}{Research Assistant}{Robotics Institute, Carnegie Mellon University}{Pittsburgh, PA}{}{}
\cvlistitem{Wrote high-performance C++ code to help with computer vision research into action recognition in video.}
\cvlistitem{Analyzed program data by repeated experiments using the Condor framework.}

\section{Education}
\cventry{May 2009}{Bachelor of Science in Computer Science}{Carnegie Mellon University}{Pittsburgh, PA}{}{}
\cvline{Selected Courses:}{Computer Networks, Secure Programming, Artificial Intelligence: Machine Learning, Computer Graphics, Algorithm Design and Analysis, Computational Physics}
\cvline{Minor:}{Physics}
% TODO: What is high school degree called?
\cventry{June 2004}{\textcolor{red}{High School Degree?}}{Strath Haven High School}{Wallingford, PA}{}{}
\end{document}
